### 2021-09-21 manuscript/manuscript.Rmd
minor edits

keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
wordcount         : "1,634"

@@

After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics. We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check. This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).     
Our main findings are displayed in Figure 1. Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`. For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.   
In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). Figure 2 further clarifies the sway of multi-analyst vs. single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions. It is worth noting on the basis of Figure 2 and a post-hoc one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs within the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.

>>>>

keywords          : "Crowd science, Many analysts, Multi-analyst, Variability, Research credibility"
wordcount         : "1,702"

@@

After two weeks of data collection, we recorded `r n_recorded` responses in Qualtrics. We excluded `r n_more_than_once` observations from participants who attempted to take the survey more than once, `r n_screened_out` participants who were screened out prior to starting the survey or did not consent, and `r n_failed_attention` participants who failed the attention check. This left us with a total sample of `r nrow(df)` participants (`r ns_bycondition[1]`, `r ns_bycondition[2]`, and `r ns_bycondition[3]` in the single-analyst, multi-consistent, and multi-inconsistent condition, respectively).     
Our main findings are displayed in Figure 1. Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, `r results(Final_beliefs)`, and the multi-inconsistent condition, `r results(Final_beliefs, "Inconsistent")`; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, `r results(Credibility, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Credibility)`; (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, `r results(Confidence, "Inconsistent")`, while it was not significantly different in the multi-consistent condition, `r results(Confidence)`; (4) ratings of bias were significantly greater in the multi-inconsistent condition, `r results(Bias, "Inconsistent")`, while they were not significantly different in the multi-consistent condition, `r results(Bias)`; and (5) ratings of error were significantly greater in both the multi-consistent condition, `r results(Error)`, and the multi-inconsistent condition, `r results(Error, "Inconsistent")`. For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, `r results(Discretion)`, and the multi-inconsistent condition, `r results(Discretion, "Inconsistent")`.   
In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). Figure 2 further clarifies the sway of multi-analyst vs. single-analyst studies, by displaying the distribution of prior and posterior beliefs across the three conditions.  
It is worth noting on the basis of Figure 2 and a post-hoc, one-sample *t*-test that, while multi-analyst studies with consistent results perform worse or no better than single-analyst studies on all measures, there is a significant, positive effect of the findings on posterior beliefs *within* the multi-consistent condition: i.e., beliefs in the research hypothesis are greater after reading the study results, `r t_apa$full_result`.
